working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-13 Manuscript_draft/Manuscript_draft.Rmd
edits

The traits measured for each species were pollen per anther, pollen size, number of ovules and stigma, style, ovary width and length. For the stigma, the stigmatic area was also measured and moreover the stigmas were divided in wet/dry type with the help of the stereomicroscope. All the morphometrical measurements were performed with a stereophotomicroscope with the exception of pollen size that was carried out with a light microscope. Pollen was counted for 20 anthers of each species with 4 replicates per sample with an hemocytometer. Previously, anthers were squashed on a known solution with the pippete tip and homogeneize with a vortex for 30 seconds. Ovule number was counted with the help of a stereomicroscope and a small grid over a petri dish from 15 randomly selected flowers. Fruits per number of flowers treated were counted for just Solanaceae species with fleshy fruit. For all the species we counted the number of seeds produced per average number of ovules. Levels of self-incompatibility were estimated by dividing the fruit set of hand self-pollination by hand cross pollination @lloyd1992.

@@

To compare the magnitude of effect of heterospecific pollen across species we conducted standarized Hedges' d [(mean of mixed 50% mix - mean of cross pollination)/pooled SD]. We did in three different ways: effect sizes of each donor per focal species; effect sizes per family of the different donors per focal species; effect sizes of all the donors grouped per focal species.

In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test in R (Vegan package, Euclidean distance) between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits. Heterospecific pollen effect was obtained through the subtraction of seed production by hand cross-pollination minus seed production of the different heterospecific pollen treatments. To find a model with the best explanatory traits we used the function **bioenv** from R. We also conducted Mantel test between the matrix of heterospecific pollen effect and the distance matrix from all the traits. Moreover, we explored also the correlation between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect and the explanatory variable the different traits. In addition, we tested the correlation between the total amount of pollen deposited on the stigma with heterospecific pollinations and the stigma size through Pearson's correlation.

@@

@@

[Add pollen on stigma counts to methods](Jose)

[Next bit to results, also divided it with ]

@@

Add effect sizes to analysis!!

Mention that SI index is calculated (Schoen & Lloyd 1984)

>>>>

The traits measured for each species were pollen per anther, pollen size, number of ovules and stigma, style, ovary width and length. For the stigma, the stigmatic area was also measured and moreover the stigmas were divided in wet/dry type with the help of the stereomicroscope. All the morphometrical measurements were performed with a stereophotomicroscope with the exception of pollen size that was carried out with a light microscope. Pollen was counted for 20 anthers of each species with 4 replicates per sample with an hemocytometer. Previously, anthers were squashed on a known solution with the pippete tip and homogeneize with a vortex for 30 seconds. Ovule number was counted with the help of a stereomicroscope and a small grid over a petri dish from 15 randomly selected flowers. Fruits per number of flowers treated were counted for just Solanaceae species with fleshy fruit. For all the species we counted the number of seeds produced per average number of ovules. Levels of self-incompatibility were estimated by dividing the seed set of hand self-pollination by hand cross-pollination @lloyd1992.

@@

To compare the magnitude of effect of heterospecific pollen across species we conducted standarized Hedges' d [(mean of mixed 50% mix - mean of cross pollination)/pooled SD] with **effsize** package. We did in three different ways: effect sizes of each donor per focal species; effect sizes per family of the different donors per focal species; effect sizes of all the donors grouped per focal species.

@@

In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test in R (**vegan** package, Euclidean distance) between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits. Heterospecific pollen effect was obtained through the subtraction of seed production by hand cross-pollination minus seed production of the different heterospecific pollen treatments. To find a model with the best explanatory traits we used the function **bioenv** from R. We also conducted Mantel test between the matrix of heterospecific pollen effect and the distance matrix from all the traits. Moreover, we explored also the correlation between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect and the explanatory variable the different traits. In addition, we tested the correlation between the total amount of pollen deposited on the stigma with heterospecific pollinations and the stigma size through Pearson's correlation.

@@

@@

### 2019-03-13 Manuscript_draft/Manuscript_draft.tex
edits

The traits measured for each species were pollen per anther, pollen
size, number of ovules and stigma, style, ovary width and length. For
the stigma, the stigmatic area was also measured and moreover the
stigmas were divided in wet/dry type with the help of the
stereomicroscope. All the morphometrical measurements were performed
with a stereophotomicroscope with the exception of pollen size that was
carried out with a light microscope. Pollen was counted for 20 anthers
of each species with 4 replicates per sample with an hemocytometer.
Previously, anthers were squashed on a known solution with the pippete
tip and homogeneize with a vortex for 30 seconds. Ovule number was
counted with the help of a stereomicroscope and a small grid over a
petri dish from 15 randomly selected flowers. Fruits per number of
flowers treated were counted for just Solanaceae species with fleshy
fruit. For all the species we counted the number of seeds produced per
average number of ovules. Levels of self-incompatibility were estimated
by dividing the fruit set of hand self-pollination by hand cross
pollination Lloyd and Schoen (1992).

@@

To compare the magnitude of effect of heterospecific pollen across
species we conducted standarized Hedges' d {[}(mean of mixed 50\% mix -
mean of cross pollination)/pooled SD{]}. We did in three different ways:
effect sizes of each donor per focal species; effect sizes per family of
the different donors per focal species; effect sizes of all the donors
grouped per focal species.

In order to test the relative effect of traits on seed production with
foreign pollen we performed Mantel test in R (Vegan package, Euclidean
distance) between the assymetrical matrix of heterospecific pollen
effect (10 by 10 matrix) with the different distance matrices of traits.
Heterospecific pollen effect was obtained through the subtraction of
seed production by hand cross-pollination minus seed production of the
different heterospecific pollen treatments. To find a model with the
best explanatory traits we used the function \textbf{bioenv} from R. We
also conducted Mantel test between the matrix of heterospecific pollen
effect and the distance matrix from all the traits. Moreover, we
explored also the correlation between traits and heterospecific pollen
effect through generalized mixed models where the response variable was
heterospecific pollen effect and the explanatory variable the different
traits. In addition, we tested the correlation between the total amount
of pollen deposited on the stigma with heterospecific pollinations and
the stigma size through Pearson's correlation.

@@

@@

\href{Jose}{Add pollen on stigma counts to methods}

{[}Next bit to results, also divided it with {]}

@@

Add effect sizes to analysis!!

Mention that SI index is calculated (Schoen \& Lloyd 1984)

>>>>

The traits measured for each species were pollen per anther, pollen
size, number of ovules and stigma, style, ovary width and length. For
the stigma, the stigmatic area was also measured and moreover the
stigmas were divided in wet/dry type with the help of the
stereomicroscope. All the morphometrical measurements were performed
with a stereophotomicroscope with the exception of pollen size that was
carried out with a light microscope. Pollen was counted for 20 anthers
of each species with 4 replicates per sample with an hemocytometer.
Previously, anthers were squashed on a known solution with the pippete
tip and homogeneize with a vortex for 30 seconds. Ovule number was
counted with the help of a stereomicroscope and a small grid over a
petri dish from 15 randomly selected flowers. Fruits per number of
flowers treated were counted for just Solanaceae species with fleshy
fruit. For all the species we counted the number of seeds produced per
average number of ovules. Levels of self-incompatibility were estimated
by dividing the seed set of hand self-pollination by hand
cross-pollination Lloyd and Schoen (1992).

@@

To compare the magnitude of effect of heterospecific pollen across
species we conducted standarized Hedges' d {[}(mean of mixed 50\% mix -
mean of cross pollination)/pooled SD{]} with \textbf{effsize} package.
We did in three different ways: effect sizes of each donor per focal
species; effect sizes per family of the different donors per focal
species; effect sizes of all the donors grouped per focal species.

@@

In order to test the relative effect of traits on seed production with
foreign pollen we performed Mantel test in R (\textbf{vegan} package,
Euclidean distance) between the assymetrical matrix of heterospecific
pollen effect (10 by 10 matrix) with the different distance matrices of
traits. Heterospecific pollen effect was obtained through the
subtraction of seed production by hand cross-pollination minus seed
production of the different heterospecific pollen treatments. To find a
model with the best explanatory traits we used the function
\textbf{bioenv} from R. We also conducted Mantel test between the matrix
of heterospecific pollen effect and the distance matrix from all the
traits. Moreover, we explored also the correlation between traits and
heterospecific pollen effect through generalized mixed models where the
response variable was heterospecific pollen effect and the explanatory
variable the different traits. In addition, we tested the correlation
between the total amount of pollen deposited on the stigma with
heterospecific pollinations and the stigma size through Pearson's
correlation.

@@

@@
